R Notebook

### 2021-06-07 paper-calculations.Rmd
corrected figure

```{r}
selectivv[[1]] %>%
  mutate(month = as.Date(paste('15', month), format='%d %b %Y')) %>%
  gather(apps, vals, -month) %>%
  filter(vals > 0 ) %>%
  mutate(przewoz = apps %in% c("uber_driver", "bolt_driver", 
                               "i_taxi_kierowca_k3", "free_now_for_drivers"),
         przewoz = ifelse(przewoz, "Kierowcy (przewóz osób)", "Dostawcy (przewóz towarów)")) %>%
  mutate(apps = case_when(apps == "bolt_courier" ~"Bolt Courier",
                          apps == "bolt_driver" ~ "Bolt Driver",
                          apps == "free_now_for_drivers" ~ "Free Now",
                          apps == "glover" ~ "Glover",
                          apps == "i_taxi_kierowca_k3" ~ "iTaxi",
                          apps == "takeaway_com_courier" ~ "Takeaway",
                          apps == "uber_driver" ~ "Uber",
                          apps == "wolt_courier_partner" ~ "Wolt"),
         label = if_else(month == max(month), as.character(apps), NA_character_)) %>%
  ggplot(data = ., aes(x = month, y = vals/1000, color = apps, group = apps)) +
  geom_line(show.legend = FALSE) + 
  geom_text_repel(aes(label = label),
                  nudge_x = -0.25, 
                  direction = "y", 
                  hjust = "left",
                  box.padding = .1,
                  force = .8,
                  na.rm = TRUE,
                  show.legend = FALSE) + 
  scale_color_brewer(type = "qual", palette = "Dark2") + 
  labs(x = "Period", y = 'Number of users (thousands)', color = "App") + 
  facet_wrap(~przewoz, scales = "free_y") +
  scale_x_date(limits = c(as.Date("2018-01-01"), as.Date("2021-09-01"))) + 
  theme(strip.text = element_text(size = 15)) ->  p1

>>>>

```{r}
selectivv[[1]] %>%
  mutate(month = as.Date(paste('15', month), format='%d %b %Y')) %>%
  gather(apps, vals, -month) %>%
  filter(vals > 0 ) %>%
  mutate(przewoz = apps %in% c("uber_driver", "bolt_driver", 
                               "i_taxi_kierowca_k3", "free_now_for_drivers"),
         przewoz = ifelse(przewoz, "Transportation", "Delivery"),
         przewoz = factor(przewoz, c("Transportation", "Delivery"))) %>%
  mutate(apps = case_when(apps == "bolt_courier" ~"Bolt Courier",
                          apps == "bolt_driver" ~ "Bolt Driver",
                          apps == "free_now_for_drivers" ~ "Free Now",
                          apps == "glover" ~ "Glover",
                          apps == "i_taxi_kierowca_k3" ~ "iTaxi",
                          apps == "takeaway_com_courier" ~ "Takeaway",
                          apps == "uber_driver" ~ "Uber",
                          apps == "wolt_courier_partner" ~ "Wolt"),
         label = if_else(month == max(month), as.character(apps), NA_character_)) %>%
  ggplot(data = ., aes(x = month, y = vals/1000, color = apps, group = apps)) +
  geom_line(show.legend = FALSE) + 
  geom_text_repel(aes(label = label),
                  nudge_x = -0.25, 
                  direction = "y", 
                  hjust = "left",
                  box.padding = .1,
                  force = .8,
                  na.rm = TRUE,
                  show.legend = FALSE) + 
  scale_color_brewer(type = "qual", palette = "Dark2") + 
  labs(x = "Period", y = 'Number of users (thousands)', color = "App") + 
  facet_wrap(~przewoz, scales = "free_y") +
  scale_x_date(limits = c(as.Date("2018-01-01"), as.Date("2021-09-01"))) + 
  theme(strip.text = element_text(size = 15)) ->  p1
